Graphics

### 2020-06-19 individual-cohorts/graphics_t_statistics.Rmd
add AD outgroup and pvclust

cor <- cor(df_one)
# clustering based on distance
hcl <- pvclust(cor)
# plot clustering
plot(hcl, hang=-1)
col2 <- colorRampPalette(rev(c("#67001F", "#B2182B", "#D6604D", "#F4A582",
                           "#FDDBC7", "#FFFFFF", "#D1E5F0", "#92C5DE",
                           "#4393C3", "#2166AC", "#053061")))
corrplot(reorder, col = col2(200))
```

@@

cor <- cor(df_two)
# clustering based on distance
hcl <- pvclust(cor)
# plot clustering
plot(hcl, hang=-1)
corrplot(reorder, col = col2(200))
```

@@

cor <- cor(df_three)
# clustering based on distance
hcl <- pvclust(cor)
# plot clustering
plot(hcl, hang=-1)
corrplot(reorder, col = col2(200))
```

>>>>

cor <- cor(df_one)
# clustering based on distance
hcl = hclust(as.dist(1-cor))
# reorder based on clustering
reorder = cor[hcl$order, hcl$order]
results <- pvclust(cor)
# plot clustering
plot(results, hang=-1)
col2 <- colorRampPalette(rev(c("#67001F", "#B2182B", "#D6604D", "#F4A582",
                           "#FDDBC7", "#FFFFFF", "#D1E5F0", "#92C5DE",
                           "#4393C3", "#2166AC", "#053061")))
corrplot(reorder, col = col2(200))
```

@@

cor <- cor(df_one)
# clustering based on distance
hcl = hclust(as.dist(1-cor))
# reorder based on clustering
reorder = cor[hcl$order, hcl$order]
results <- pvclust(cor)
# plot clustering
plot(results, hang=-1)
corrplot(reorder, col = col2(200))
```

@@

cor <- cor(df_one)
# clustering based on distance
hcl = hclust(as.dist(1-cor))
# reorder based on clustering
reorder = cor[hcl$order, hcl$order]
results <- pvclust(cor)
# plot clustering
plot(results, hang=-1)
corrplot(reorder, col = col2(200))
```
